---
title: "PSY 8712 Week 8 Project"
author: "Julia Hong"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    number_sections: true
knit: (function(inputFile, encoding) {rmarkdown::render(inputFile, encoding = encoding, output_dir = "../out")})
---

# **Reproducible Image and Online Resources**

An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](https://mybinder.org).

An interactive web app is available by [clicking this link instead](https://shinyapp.io).

# **Script Settings and Resources**

```{r echo = FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(kableExtra)
```

# **Data Import and Cleaning**

Import data from week3.csv, add labels for gender and condition, reverse code Q5, compute mean scores for Q1-Q6 and Q8-Q10

```{r echo = FALSE}
week8_tbl <- read_csv("../data/week3.csv", col_names = TRUE, col_types = cols(timeStart=col_datetime("%F %h:%M:%S"))) %>%
  mutate(
    gender = factor(gender, levels = c("M", "F"), labels = c("Male", "Female")),
    condition = factor(condition, levels = c("A", "B", "C"), labels = c("Block A", "Block B", "Control")),
    q5 = 6 - q5,
    x_bar = rowMeans(across(q1:q6)),
    y_bar = rowMeans(across(q8:q10))
  )
```

# **Visualization**

Visualize data with kable and create scatterplot for mean scores

```{r echo = FALSE}
week8_tbl %>% 
  select(q1:q6) %>% 
  kable()

week8_tbl %>%
  ggplot(mapping = aes(x = x_bar, y = y_bar)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method = "lm", se = TRUE, fill = "purple")
```


# **Analysis**

Calculate correlation between x_bar and y_bar

```{r}
corr <- cor.test(x = week8_tbl$x_bar, y = week8_tbl$y_bar)
corr
```

I observed a correlation of `r sub("^0\\.", ".", round(corr$estimate, 2))`, which is insignificant at an alpha of .05, so we fail to reject the null hypothesis that the correlation is equal to 0.

# **Data Export**

Export dataset for shiny including timeStart, gender, x_bar, and y_bar variables

```{r}
week8_tbl %>%
  select(timeStart, gender, x_bar, y_bar) %>%
  saveRDS(file = "../shiny_week8/week8_shiny.rds")
```